\documentclass[line, margin]{res}
\usepackage[charter]{mathdesign}
\usepackage{url}
\usepackage[usenames,dvipsnames,svgnames]{xcolor}
\usepackage[none]{hyphenat}

\begin{format}
\title{l}\\
\employer{l}\dates{r}\\
\body\\
\end{format}

\begin{document}
\newsectionwidth{1in}

\name{\Large \sc Sergey Karayev}
\address{\small{\textcolor{MidnightBlue}{https://sergeykarayev.com} $\cdot$ \textcolor{MidnightBlue}{sergeykarayev@gmail.com} $\cdot$ Updated 2018 October 6}}

\begin{resume}
\section{\sc Objective}
Develop and deploy AI systems to improve human life.

\section{\sc Education}
\begin{description}
\item[{\bf University of California, Berkeley}] $\cdot$ {\it August 2009 - December 2014}
\\Ph.D. Computer Science
\\\emph{Thesis Advisor}: Trevor Darrell

\item[{\bf University of Washington, Seattle}] $\cdot$ {\it September 2005 - June 2009}
\\B.S. Computer Science \& B.A. Psychology
\\\emph{Thesis Advisor}: Steven Seitz
\end{description}

\section{\sc Experience}

\title{\bf Head of AI for STEM}
\employer{\it Turnitin, Oakland, CA}
\dates{\it October 2018 - present}
\begin{position}
Gradescope was acquired as a standalone product by Turnitin, a leading educational technology company that has previously focused on assessment of writing.
My role is to accelerate development of AI technologies for STEM assessment.
\end{position}

\title{\bf Instructor and Organizer}
\employer{\it https://fullstackdeeplearning.com/bootcamp}
\dates{\it August 2018}
\begin{position}
As part of Gradescope, and with two other instructors, developed materials for and organized a 3-day bootcamp program for software developers familiar with deep learning to get first-hand experience with the best practices of all components of a DL project.
\end{position}

\title{\bf Co-founder, Director of AI}
\employer{\it Gradescope, Berkeley, CA}
\dates{\it September 2014 - October 2018}
\begin{position}
Gradescope enables instructors to grade paper-based exams, online homework, and programming projects on one platform, with AI assistance.
Over 60M student answers at over 600 schools were graded on our platform.
\end{position}

\title{\bf Graduate Student Researcher}
\employer{\it UC Berkeley}
\dates{\it September 2009 - September 2014}
\begin{position}
Thesis work on novel application of reinforcement learning techniques to the task of object recognition.
Contributed to the development of Caffe, a popular deep learning frameworks.
Developed a 3D perception dataset and method, and a novel hierarchical generative model.
\end{position}

\title{\bf Research Intern}
\employer{\it Creative Tech. Lab at Adobe, San Francisco, CA}
\dates{\it Summer 2013}
\begin{position}
Developed a system for recognizing the style of photographs and paintings.
\end{position}

\title{\bf Graduate Student Instructor}
\employer{\it University of California, Berkeley}
\dates{\it Fall 2012, Fall 2013}
\begin{position}
Led section and composed exams for the CS 188 Intro to AI course.
\end{position}

\title{\bf Research and Development Intern}
\employer{\it Artsy, New York City, NY}
\dates{\it Summer 2012}
\begin{position}
Prototyped a system for the recognition of visual properties of artwork.
\end{position}

\title{\bf Undergraduate Researcher}
\employer{\it University of Washington}
\dates{\it October 2007 - June 2009}
\begin{position}
Worked on augmented reality on the iPhone and human-computer interaction via webcam.
\end{position}

\title{\bf Software Development Intern}
\employer{\it Zillow.com, Seattle, WA}
\dates{\it Summer 2008}
\begin{position}
Maintained, improved, and added features for a high-traffic consumer website.
\end{position}

\title{\bf Teaching Assistant}
\employer{\it University of Washington}
\dates{\it Winter 2007, Spring 2007}
\begin{position}
Led section and graded for the introductory programming course, CSE 142.
\end{position}

\title{\bf Research Apprentice}
\employer{\it Friday Harbor Laboratories (UW)}
\dates{\it Spring 2006}
\begin{position}
Explored the distribution of neuropeptides in a sea slug central nervous system.
\end{position}

\section{\sc Skills}
AI: Deep Learning, Computer Vision, System Deployment\\
Scientific and data: Python, Matlab, C/C++\\
Web development: Ruby, JavaScript\\
Some code is open-source at \textcolor{MidnightBlue}{http://github.com/sergeyk}\\
Fluent in Russian.

% \newpage

\section{\sc Publications}

\textbf{How Do Professors Format Exams? An Analysis of Question Variety at Scale} at \emph{L@S 2018}\\
Paul Laskowski, \underline{Sergey Karayev}, Marti Hearst

\textbf{Gradescope: A Fast, Flexible, and Fair System for Scalable Assessment} at \emph{L@S 2017}\\
Arjun Singh, \underline{Sergey Karayev}, Kevin Gutowski, Pieter Abbeel

\textbf{Anytime Recognition of Objects and Scenes} at \emph{CVPR 2014} (oral)\\
\underline{Sergey Karayev}, Mario Fritz, Trevor Darrell

\textbf{Recognizing Image Style} at \emph{BMVC 2014}\\
\underline{Sergey Karayev}, Matthew Trentacoste, Helen Han, Aseem Agarwala, Trevor Darrell, Aaron Hertzmann, Holger Winnem\"{o}ller

\textbf{Caffe: Convolutional Architecture for Fast Feature Embedding} at \emph{ACM MM 2014}\\
Yangqing Jia, Evan Shelhamer, Jeff Donahue, \underline{Sergey Karayev},
Jonathan Long, Ross Girshick, Sergio Guadarrama, Trevor Darrell

\textbf{Dynamic Feature Selection for Classification on a Budget} at \emph{ICML-W 2013}\\
\underline{Sergey Karayev}, Mario Fritz, Trevor Darrell

\textbf{A Category-Level 3-D Object Dataset: Putting the Kinect to Work} at \emph{ICCV-W 2013}\\
Allison Janoch, \underline{Sergey Karayev}, Yangqing Jia, Jonathan T. Barron, Mario Fritz, Kate Saenko, Trevor Darrell

\textbf{Timely Object Recognition} at \emph{NIPS 2012}\\
\underline{Sergey Karayev}, Tobias Bamgartner, Mario Fritz, Trevor Darrell

\textbf{3-D Object Detection Using Category and Instance-level Appearance Models} at \emph{IROS 2011}\\
Kate Saenko, \underline{Sergey Karayev}, Yangqing Jia, Alex Shyr, Allison Janoch, Jon Long, Mario Fritz, Trevor Darrell

\textbf{A Probabilistic Model for Recursive Factorized Image Features} at \emph{CVPR 2011}\\
\underline{Sergey Karayev}, Mario Fritz, Sanja Fidler, Trevor Darrell

\textbf{An Additive Latent Feature Model for Transparent Object Recognition} at \emph{NIPS 2009}\\
Mario Fritz, Michael Black, Gary Bradski, \underline{Sergey Karayev}, Trevor Darrell

% \section{\sc Service}
% {\bf CSGSA Officer}: Industry Liaison for the Berkeley CS Graduate Association. \emph{May 2012 - 2014}
% % \\{\bf After-school program volunteer}: tutor low-income 4th and 5th grade kids. \emph{Fall 2010}
% \\{\bf Graduate Assembly Delegate}: represented the department. \emph{2010}

\section{\sc Awards}
{\bf Mark Everingham Prize} (for work on the Caffe open source software), 2017\\
{\bf National Defense Science and Eng. Grad. Fellowship} (full tuition and stipend), 2009-2012\\
{\bf Mary Gates Research Scholarship} (undergraduate research stipend), 2008\\
{\bf Microsoft Scholarship} (CS department award), 2008\\
{\bf Honors Bordeaux Scholarship} (full tuition for one year), 2008\\
%{\bf Phi Beta Kappa}, 2007-present\\
{\bf Mary Gates Honors Scholarship} (full tuition for three years), 2005-2007\\
{\bf Robert C. Byrd Honors Scholarship} (Washington State award), 2005-2009\\
{\bf National Merit Scholarship} (sponsored by the Boeing Company), 2005-2009\\
{\bf Undergraduate Academic Excellence Scholarship} (UW award), 2005.

\end{resume}
\end{document}
